Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-23 vesicle_code/docs/permeableVes/main.tex
converting stenosis to pdf
fixed up some figures and did some todos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}
\todo[inline]{put a vertical dashed line at the times when permeability
starts to be important. Convert to physical time.}

@@

Our simulations indicate the semi-permeability does affect the excess
pressure, and the vesicle's reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
\todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}
\todo[inline]{Membrane tension. Look at each of the five cases and find
the instance where tension reaches its max value. Plot the tension as
the colorbar along the vesicle shape.}

@@

\begin{itemize}
  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s
  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s
  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s
  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s
  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
    plot (i))
\end{itemize}
\todo[inline]{Center of mass vs.~time}
\todo[inline]{Membrane tension. Look at each of the five cases and find
the instance where tension reaches its max value. Plot the tension as
the colorbar along the vesicle shape.}

\begin{figure*}[htp]
  \centering
%  \ifTikz
  \input{figures/contractingComposite.tikz}
%  \else
%  \includegraphics{figures/contractingComposite.pdf}
%  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c) The ability for a semi-permeable vesicle to pass through the
  constriction depends on the semi-permeability rate. (d--f) The ability
  for a semi-permeable vesicle to pass through the constriction depends
  on the flow rate. (g) A semi-permeable vesicle passing through six
  periods of the constricting geometry. (h) The reduced area with the
  marks representing shapes in (g). (i) The vesicle velocity with the
  marks representing shapes in (g).}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}

@@

Our simulations indicate the semi-permeability does affect the excess
pressure, and the vesicle's reduced area reduces by about 6.1\%
(Figure~\ref{fig:stenosisComposite}(d)). Since the area does decrease at
a constant rate we expect that a larger amounts of deflation is possible
if the vesicle is stenosed for a longer period of time. Therefore, in
Figure~\ref{fig:stenosisComposite}(b), we consider a vesicle passing
through a channel of double the length, and we observe that the reduced
area decreases by 13.2\% (Figure~\ref{fig:stenosisComposite}(e)).
\todo[inline]{This example also used a smaller flow rate of $8.4\mu$m/s}

@@

\begin{itemize}
  \item Vesicle velocity in plot (a) varies from 5 to 24 microns/s.
  \item Vesicle velocity in plot (b) varies from 5 to 28 microns/s. Time
    that vesicle first completely passes through constriction is 4.75s
  \item Vesicle velocity in plot (c) varies from 0.2 to 2 microns/s.
  \item Vesicle velocity in plot (d) varies from 5 to 25 microns/s. Time
    that vesicle first completely passes through constriction is 4.76s
  \item Vesicle velocity in plot (g) varies from 14 to 95 microns/s (see
    plot (i)). Time that vesicle first completely passes through
    constriction is 1.43s
\end{itemize}

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c) The ability for a semi-permeable vesicle to pass through the
  constriction depends on the semi-permeability rate. (d--f) The ability
  for a semi-permeable vesicle to pass through the constriction depends
  on the flow rate. (g) A semi-permeable vesicle passing through six
  periods of the constricting geometry. (h) The reduced area with the
  marks representing shapes in (g). (i) The vesicle velocity with the
  marks representing shapes in (g).}
\end{figure*}
